\cvsection{Certifications}
\begin{cventries}
  \cventry
    {Data Structure \hspace{12cm}Design and Analysis of Algorithm \hspace{10cm} Computer Network}
     {Microsoft Research}
    {Online}
    {Jan 2015-July 2015}
    {
      \begin{cvitems}
        \item {Administered by Microsoft Research, Bangalore, India}
      \end{cvitems}
    }
    \cventry
    {Maintaining Cyber Security}
    {DeVry University}
    {Online}
    {June,2015 }
    {
      \begin{cvitems}
        \item {Administered by DeVry University,US}
      \end{cvitems}
    }
        \cventry
    {C with Data Structure}
    {TCS}
    {Cert. No. ENT/1595/54038/2016006684 }
    {July 2015 - Sept 2015 }
    {
      \begin{cvitems}
        \item {Administered by ION \& Tata Consultancy Services, Pune, India}
      \end{cvitems}
    }
      \cventry
    {Microsoft Sql Server}
    {Udemy}
    {Cert. No. UC-JCJMD70E }
    {July 2015}
    {
     % \begin{cvitems}
      %  \item {Administered by ION \& Tata Consultancy Services, Pune, India}
      %\end{cvitems}
    }
      \cventry
    {Business Email}
    {HP}
    {Cert. Serial 1549150 - 401}
    {Aug 2015 }
    {
      \begin{cvitems}
       \item {Recognize the do's and dont's of business email}
      \end{cvitems}
    }
    
      \cventry
    {Strategic Planning}
    {HP}
    {Cert. Serial 1549150 - 40540}
    {Aug 2015 }
    {
      \begin{cvitems}
        \item {Using a SWOT (Strengths, Weaknesses, Opportunities, and Threats) analysis for choosing the best strategies to help a business reach its long-term goals.}
      \end{cvitems}
    }
    \cventry
    {HTML}
    {Udemy \& Vigoma Technologies}
    {Cert. Serial UC-F9T09L91F}
    {Sept 2015 }
    {
      \begin{cvitems}
       \item {Building  Web pages with an Interactive Design}
      \end{cvitems}
    }
    \cventry
    {Beginning Oracle WebLogic}
    {Udemy}
    {Cert. No. UC-M8X0RJ9L}
    {Sept 2015 }
    {
      \begin{cvitems}
       \item {Web Page Database to Server}
      \end{cvitems}
    }
    \cventry
    {Java Script \& J Query}
    {Udemy}
    {Cert. No. UC-SPOQRZRN}
    {Sept 2015 }
    {
      \begin{cvitems}
       \item {Implementations of client-side scripts to interact with the user.}
      \end{cvitems}
    }
    \cventry
    {Presenting Data}
    {HP}
    {Cert. Serial CJ\_67Ue}
    {Jan 2016 }
    {
      \begin{cvitems}
        \item {Effective Presentation of data by specific chart type decision making.}
      \end{cvitems}
    }
    \cventry
    {Social Media Marketing}
    {HP}
    {Cert. Serial P6j\_C\_q8}
    {Jan 2016 }
    {
      \begin{cvitems}
        \item {Explore a range of different social media marketing campaigns.}
      \end{cvitems}
    }
\end{cventries}
